---
title: "Lab 5 "
author: "Ruixuan Hu"
date: "11/9/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with N = 1000 and 10000.


```{r}
num <- 0

roll=function(N){
  for (i in (i:N)) {
    dice_roll <-sample(1:6, times,replace = TRUE)
    if(dice_roll[1]==6 | dice_roll[2]==6 | dice_roll[3]==6 | dice_roll[4]==6) 
      num=num + 1
  }
  proportion = num/N
  return(proportion)
}

roll(1000)
roll(10000)

```


2.Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element.
Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.


```{r}

find_small = function(x) {
small_ele=x[1]
index=1
  for(num in 2:length(x)) {
    if (x[num] < small_ele) {
      small_ele =x[num]
      index = num 
    }  
    
  }
outcome=(c(small_ele,index))
return(outcome)

}

find_small(c(1,4,2,0,5))


```

